---
title: "Homework 7"
author: "Suresh Bhavsar"
date: "2025-04-14"
output: pdf_document
---

Name: Suresh Bhavsar
UT EID: sb65245
GitHub repo: https://github.com/Surbeast/sds-315-hw-8


```{r global_options, echo=FALSE, message=FALSE, warning=FALSE, results='hide', include=FALSE}
knitr::opts_chunk$set(warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60), echo = FALSE, fig.align = "center", out.width = "100%", message = FALSE, warning = FALSE)

library(ggplot2)
library(tidyverse)
library(mosaic)
library(MatchIt)
```

# Problem 1: Regression Warm Up

## Part A
``` {r, include=FALSE}
creatine <- read_csv('creatinine.csv')

creatine_lm = lm(creatclear ~ age, data = creatine)

coef(creatine_lm)
```

A 55 year old should expect a creatinine clearance of 113.71. I fit the data to a linear regression model and got the equation creatinine = 147.81 - 0.62 * age. By plugging in 55 for the age we get the expected creatinine cleartance for a 55 year old. 

## Part B

The creatinine clearance rate decreases at 0.62 ml/minute per year. I fit the data to a linear regression model and determined the slope of the equation to determine the rate of change for creatinine clearance.

## Part C

The expected creatinine clearance for a 40 year old is determined by the expression 147.81 - 0.62 * 40, which evaluates to 123.01. The 40 year old therefore has a creatinine clearance 11.99 higher than expected. The expected creatinine clearance for a 60 year old is determined by the expression 147.81 - 0.62 * 60, which evaluates to 110.61. The 60 year old therefore has a creatinine clearance 1.39 higher than expected. The 40 year old has a creatinine clearance that is healthier for their age. 

# Problem 2: Modeling Disease Growth

```{r, include=FALSE}
covid <- read_csv('covid.csv')

italy <- subset(covid, country == "Italy")
italy$log_deaths <- log(italy$deaths)
italy_model <- lm(log_deaths ~ days_since_first_death, data = italy)
coef(italy_model)

spain <- subset(covid, country == "Spain")
spain$log_deaths <- log(spain$deaths)
spain_model <- lm(log_deaths ~ days_since_first_death, data = spain)
coef(spain_model)

italy_boot = do(10000)*lm(log_deaths ~ days_since_first_death, data = mosaic::resample(italy))
confint(italy_boot, level = 0.95)

spain_boot = do(10000)*lm(log_deaths ~ days_since_first_death, data = mosaic::resample(spain))
confint(spain_boot, level = 0.95)


```
## 1

The estimated growth rate for Italy is 0.183 with a bootstrapped 95% confidence interval of (0.159, 0.208). The estimated doubling time for Italy is 3.8 days with a bootstrapped 95% confidence interval of (3.4, 4.4). 

## 2

The estimated growth rate for Spain is 0.276 with a bootstrapped confidence interval of (0.235, 0.318). The estimated doubling time for Spain is 2.5 days with a bootstrapped 95% confidence interval of (2.2, 3.0). 

## 3

```{r}
ggplot(covid, aes(x = days_since_first_death, y = deaths, color = country)) +
  geom_line() +
  labs(
    title = "Reported Daily COVID-19 Deaths Over Time",
    x = "Days Since First Death",
    y = "Reported Deaths",
    color = "Country"
  ) +
  theme_minimal()
```

# Problem 3: Price Elasticity of Demand

```{r, include=FALSE}
milk <- read.csv("milk.csv")

milk$log_price <- log(milk$price)
milk$log_sales <- log(milk$sales)

milk_model <- lm(log_sales ~ log_price, data = milk)
coef(milk_model)

boot_milk = do(10000)*lm(log_sales ~ log_price, data = mosaic::resample(milk))
confint(boot_milk, level = 0.95)
```

The estimated price elasticity of demand for milk is -1.619 with a bootstrapped 95% confidence interval of (-1.772, -1.456). To estimate the elasticity, i first took the log of both sides of the equation to effectively turn it into a linear equation with Beta being the slope. I then created a linear regression model of the log of sales based on the log of prices to estimate the price elasticity before bootstrapping repeatedly from the data to create a confidence interval. 